Open integrated distance sampling for modelling age-structured population dynamics

### 2024-07-23 Manuscript_Nilsen_Nater.qmd
Clarified treatment of stochasticity in pop. model

Note that recruitment rate $R$ is defined as juveniles/adult (not juveniles/female). We also make the simplifying assumption that there is no age- or sex-dependence of vital rates, but this assumption could be relaxed by including additional auxiliary data [@Israelsen2020; @Sandercock2011].

>>>>

Note that recruitment rate $R$ is defined as juveniles/adult (not juveniles/female). We assume no stochasticity beyond time-variation in vital rates in the model for population density itself, but instead treat local population sizes (numbers of birds in age class $a$ in year $t$ within the area of each transect $j$, $N_{a,j,t}$), as outcomes of a Poisson process with an expected average equaling $D_{a,t}$ times the transect area (see below). We also make the simplifying assumption that there is no age- or sex-dependence of vital rates, but this assumption could be relaxed by including additional auxiliary data [@Israelsen2020; @Sandercock2011].
